### 2023-12-24 ms.qmd
Updates

```{r}
#| label: setup

pacman::p_load(tidyverse, flextable, emmeans, DHARMa, brms, here, ggplot2, lme4, zoo, lmerTest, broom, tidybayes)

source("./R/1_data_process.R")
source("./R/func.r")
```

@@

Cognition is defined as the processes by which animals gather, preserve, and use information from their environment through perception, learning, memory, and decision making (@shettleworth_2009). These mechanisms underpin several aspects of animals' ecology such as habitat selection, foraging decisions, mate choice, antipredatory strategies, and/or social behaviours that are crucial for survival and reproduction (@dukas_evolutionary_2004). Particularly, learning - the acquisition of neuronal representations of new information (@dukas_evolutionary_2004) - is seen as fundamental for coping with environmental changes by allowing individuals to create new associations between events (@dukas_evolutionary_2004; @leal_behavioural_2012; @buchanan_condition_2013). However, the ability of organisms to acquire new information varies accross individuals, with this natural variation usually being influenced by factors like age, sex, social system, gut microbiota, or the environment where animals develop (**REFS**). In this regard, the latter can be particularly relevant because the brain is especially sensitive to environmental impacts during early stages of development (@zhu_prenatal_2004). 
These differences in neural development caused by early environment can have long-lasting effects on learning skills, and prenatal Glucocorticoids (GCs) and prenatal thermal environment are known to play a prominent role in shaping learning abilities in different taxa (see @lemaire_prenatal_2000; @zhu_prenatal_2004; @amiel_hotter_2012; @amiel_egg_2014; @crino_corticosterone_2014; @abayarathna_effects_2020). GCs - **hormones related to organisms' response to changes in homeostasis (BEST DEF AND REF**) - can have sustained pysiological effects on neural structure and physiology associated with animals' performance on learning tasks (**Definition and REF**). In this sense, there is evidence that high prenatal GC levels impair with learning accross different taxa (**MORE EG.S AND REFS**; @lemaire_prenatal_2000; @zhu_prenatal_2004), but results vary depending on sex, or task (**REFS**). Also, some studies have revealed effects of prenatal temperature on learning in ectotherms (**REFS**). For instance, ... (**REFS**). In this vein, the effect of prenatal temperature has been associated with similar changes in neural structure and metabolic activity (**REFS**). However, despite both prenatal GCs and thermal environment are known to affect learning through similar mechanisms, the interaction between this two factors is still poorly understood.
In this study, we aim to explore the interactive effects between prenatal Glucocorticoids (GCs) and the prenatal thermal environment on learning using two species of skinks, the delicate skink (_Lampropholis delicata_) and the common garden skink (_L. guichenoti_), as our model species. We experimentally increased Corticosterone (CORT) - the main GC in reptiles - levels in the eggs of these two species of skinks and then incubated them at two different temperatures in a 2X2 factorial design. Then, we subjected the juveniles to a colour-associative and a reversal task to explore their learning abilities. We hypothesise that changes in CORT levels and temperature during early development will have sustained effects on brain's morphology and physiology that will ultimately impact learning skills. We predicted that individuals exposed to high levels of CORT and/or low temperatures will perform worse in the learning tasks than control individuals or individuals exposed to high temperatures. We also expected incubation at high temperatures to decrease the impact of CORT on skink's performance, while cold incubation temperatures were expected to increase CORT detrimental effects on learning.

@@

We calculated $R^2$ as follows

$$
R^2 = \frac{SS_{reg}}{SS_{tot}}
$$ {#eq-r2}

@eq-r2

We have a total of `r length(unique(data$Lizard_id))`

```{r,tb1}
#| label: tbl-tb1
#| tbl-cap: "Summary of the data"

tab <- data %>% 
  group_by(Lizard_id) %>% 
  summarise(
    n = n()
  ) 
flextable(tab[2:3,])
```

>>>>

```{r}
#| label: setup
pacman::p_load(tidyverse, flextable, emmeans, DHARMa, brms, here, ggplot2, lme4, zoo, lmerTest, broom, tidybayes)
```

@@

Cognition is defined as the processes by which animals gather, preserve, and use information from their environment through perception, learning, memory, and decision making (@shet). These mechanisms underpin several aspects of animals' ecology such as habitat selection, foraging decisions, mate choice, antipredatory strategies, and/or social behaviours that are crucial for survival and reproduction (@dukas_evolutionary_2004). Particularly, learning - the acquisition of neuronal representations of new information (@dukas_evolutionary_2004) - is seen as fundamental for coping with environmental changes by allowing individuals to create new associations between events (@dukas_evolutionary_2004; @leal_behavioural_2012; @buchanan_condition_2013). However, the ability of organisms to acquire new information varies accross individuals, with this natural variation usually being influenced by factors like age, sex, social system, gut microbiota, or the environment where animals develop (**REFS**). In this regard, the latter can be particularly relevant because the brain is especially sensitive to environmental impacts during early stages of development (@zhu_prenatal_2004). 
These differences in neural development caused by early environment can have long-lasting effects on learning skills, and prenatal Glucocorticoids (GCs) and prenatal thermal environment are known to play a prominent role in shaping learning abilities in different taxa (see @lemaire_prenatal_2000; @zhu_prenatal_2004; @amiel_hotter_2012; @amiel_egg_2014; @crino_corticosterone_2014; @abayarathna_effects_2020). GCs - **hormones related to organisms' response to changes in homeostasis (BEST DEF AND REF**) - can have sustained pysiological effects on neural structure and physiology associated with animals' performance on learning tasks (**Definition and REF**). In this sense, there is evidence that high prenatal GC levels impair with learning accross different taxa (**MORE EG.S AND REFS**; @lemaire_prenatal_2000; @zhu_prenatal_2004), but results vary depending on sex, or task (**REFS**). Also, some studies have revealed effects of prenatal temperature on learning in ectotherms (**REFS**). For instance, ... (**REFS**). In this vein, the effect of prenatal temperature has been associated with similar changes in neural structure and metabolic activity (**REFS**). However, despite both prenatal GCs and thermal environment are known to affect learning through similar mechanisms, the interaction between this two factors is still poorly understood.
In this study, we aim to explore the interactive effects between prenatal Glucocorticoids (GCs) and the prenatal thermal environment on learning using two species of skinks, the delicate skink (_Lampropholis delicata_) and the common garden skink (_L. guichenoti_), as our model species. We experimentally increased Corticosterone (CORT) - the main GC in reptiles - levels in the eggs of these two species of skinks and then incubated them at two different temperatures in a 2X2 factorial design. Then, we subjected the juveniles to a colour-associative and a reversal task to explore their learning abilities. We hypothesise that changes in CORT levels and temperature during early development will have sustained effects on brain's morphology and physiology that will ultimately impact learning skills. We predicted that individuals exposed to high levels of CORT and/or low temperatures will perform worse in the learning tasks than control individuals or individuals exposed to high temperatures. We also expected incubation at high temperatures to decrease the impact of CORT on skink's performance, while cold incubation temperatures were expected to increase CORT detrimental effects on learning.

@@
